%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Android Developer} % Job title
    {Emirates} % Organization
    {Dubai, UAE} % Location
    {Nov. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical improvements of data layer, migration to kotlin.}
\item {Rewrote \textit{My Trips} following \textit{backend for frontend} approach.}
        \item {Helped with the recrutiment and mentioned new Android developers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Android Developer} % Job title
    {Tigerspike} % Organization
    {Dubai, UAE} % Location
    {Oct. 2017 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented new modules within existing application.}
        \item {Had big impact on technical improvement of legacy code.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Developer} % Job title
    {Amistad Mobile} % Organization
    {Cracow, Poland} % Location
    {Jan. 2014 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed many native Android applications from scratch.}
        \item {Teamleaded in Android projects, Worked on Windows Phone and iOS projects.}
        \item {Designed and implemented multiplatform framework for rendering 3d maps which was used in iOS, Android and on web pages.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile \& Web Developer} % Job title
    {Pharmaway} % Organization
    {Cracow, Poland} % Location
    {Feb. 2013 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained web pages. Worked on Windows desktop applications designed for touch screens.}
        \item {Implemented basic quiz-game framework and used it successfuly in many Android applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
